Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-04-29 writeup/gz_hubble_data.tex
Renaming 'uncorrectable' set to 'lower limit'. Closes #48

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in Galaxy Zoo: Hubble are selected from various \textit{HST} Legacy surveys taken with the Advanced Camera for Surveys, including AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S. Galaxies are included for GZH classifications down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to sources as high as $z\simeq4$. The morphological data includes measurements of bulge vs. disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

This paper presents the results from the Galaxy Zoo Hubble (GZH) project. GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.

@@

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The coadded Stripe~82 images were assembled from runs (106,206) in DR7 and generated into JPGs using the method of \citet{lup04}.

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of $z$, $\mu$, and \pfeatures{}. To define this smooth space, we generate a convex hull that encloses the correctable and uncorrectable \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and uncorrectable regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

For the ``uncorrectable'' galaxies, those for which we cannot confidentely assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}. Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift. In each $z$,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures. We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect \pfeaturesrest{} to be for any observed value of \pfeatures.

\begin{table}
\center
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Uncorrectable                      & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), uncorrectable (green), and NEI (pink) galaxies in the full GZH sample. The uncorrectable galaxies tend towards higher redshift, slightly lower in surface brightness, and lower values of $p_{features}$ than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{figure*}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), uncorrectable (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{figure*}

@@

We corrected for the biases described for the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}. For this question, we provide the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if ``uncorrectable'', $\tt best = lower~limit$, and if neither, $\tt best = weighted$.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~uncorrectable ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrectable (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrectable (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable*}

@@

\begin{table}
\caption{Correctable fractions for the top-level task in GZH in the GOODS shallow-depth (2-epoch) images. \label{tbl:goods_shallow_categories}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                   & GOODS-N & GOODS-S & Total \\
\hline
Correctable                        & 748     & 514     & 1,262 \\
Uncorrectable                      & 526     & 1,143   & 1,669 \\
No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
NEI                                & 851     & 2,670   & 3,521 \\
No Redshift Information            & 159     & 319     & 478   \\
Total                              & 2,551   & 4,913   & 7,464 \\
\hline\hline
\end{tabular}
\end{table}

@@

\begin{table}ー
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p_bar}. Correctable images had a single-valued relationship between their measured $p_{\rm bar}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p_bar}). Uncorrectable images had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions). Only 17\% (maximum) of FERENGI galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 664   & 17\% \\
Uncorrectable                      & 483   & 12\% \\
NEI                                & 2,803     & 71\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

>>>>

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. We also describe and employ a novel method for calibrating morphological bias by using artificially-redshifted galaxy images as a baseline. This paper presents both the raw and calibrated morphological vote fractions for $150,771$ galaxies, constituting a large data set suitable for large-scale studies of galaxy evolution.

@@

This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble.

@@

The Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The coadded Stripe~82 images were assembled from runs 106 and 206 in DR7 and generated as JPGs using the method of \citet{lup04}.

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between \pfeaturesz{} and \pfeaturesrest{} by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value. We refer to galaxies in this region as the \emph{lower limit} sample. These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, we assume the true correctable region is a smooth function of $z$, $\mu$, and \pfeatures{}. To define this smooth space, we generate a convex hull that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. We use the resulting hulls to define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

For the ``lower-limit'' galaxies for which we cannot confidently assign a single debiased \pfeatures{} value, we instead determine a likely \emph{range} of debiased values, using a method visualized in Figure~\ref{fig:6c}. Here we again use the \ferengi{} simulated data to analyze the range of intrinsic \pfeaturesrest{} values for any given observed \pfeatures{} value, again as a function of surface brightness and redshift. In each $z$,$\mu$ bin, we examine the spread of intrinsic values of \pfeaturesrest{} for 4 ranges of observed \pfeatures. We quantify the range of intrinsic values as the inner 80\% of the data; this range is represented by the orange bars in Figure~\ref{fig:6c}. For any galaxy which can't be directly debiased by the $\zeta$ method, then, we use these ranges to denote the upper and lower limits on what we expect \pfeaturesrest{} to be for any observed value of \pfeatures.

\begin{table}
\center
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images have a single-valued relationship between their measured \pfeatures{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Images with only a lower-limit on \pfeatures{} have a non single-valued relationship (blue regions). NEI images have undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions).\label{tbl:ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Lower-limit                        & 1,986   & 50\% \\
NEI                                & 80      &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

@@

\begin{table*}
\caption{Correctable fractions for the top-level task in GZH, split by survey.}\label{tbl:hubble_debiasable}
\begin{tabular}{lcrrrrrrr}
\hline\hline
                                   & Correction type & AEGIS   & COSMOS & GEMS & GOODS-N & GOODS-S    & SDSS    & Total \\
\hline
Correctable                        & 0               & 1,654   & 15,170 & 1,837 & 993    & 835     	& 0       & 20,489\\
Lower-limit                        & 1               & 1,917   & 26,113 & 2,423 & 1,385  & 1,282   	& 0       & 33,120\\
No Correction Needed ($z \le 0.3$) & 2               & 955     & 11,926 & 1,175 & 415    & 400     	& 37,545  & 52,416\\ 
NEI                                & 3               & 2,847   & 34,511 & 3,308 & 2,535  & 2,523   	& 0       & 45,724\\
No Redshift Information            & 4               & 1,134   & 5,088  & 561   & 687    & 102   		& 14,316  & 21,888\\
Total                              &                 & 8,507   & 92,808 & 9,304 & 6,015  & 5,142   	& 51,861  & 173,637\\
\hline\hline
\end{tabular}
\end{table*}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample. The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of $p_{features}$ on average than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{figure*}

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/debiased_corrections.pdf}
\caption{Debiased $p_{features}$ corrected to $z=0.3$ vs weighted $p_{features}$ for the correctable (left), lower-limit (middle), and NEI (right) galaxies in the GZH sample.}
\label{fig:debiased_corrections}
\end{figure*}

@@

We corrected for the biases described for the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}. For this question, we provide the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were corrected through debiasing (\S\ref{ssec:zeta_results}), if possible. 0~=~correctable, 1~=~lower-limit ($p_{raw}$ --- $p_{adj}$ is not single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected (insufficient FERENGI galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form, as well as at \url{http://data.galaxyzoo.org}. The complete version includes data for 118,425~galaxies and morphological information for all tasks in the tree. A subset of the information is shown here to illustrate form and content.}
\end{deluxetable*}

@@

\begin{table}
\caption{Correctable fractions for the top-level task in GZH in the GOODS shallow-depth (2-epoch) images. \label{tbl:goods_shallow_categories}}
\begin{tabular}{lrrrrrrrr}
\hline\hline
                                   & GOODS-N & GOODS-S & Total \\
\hline
Correctable                        & 748     & 514     & 1,262 \\
Lower limit                        & 526     & 1,143   & 1,669 \\
No Correction Needed ($z \le 0.3$) & 267     & 267     & 534   \\ 
NEI                                & 851     & 2,670   & 3,521 \\
No Redshift Information            & 159     & 319     & 478   \\
Total                              & 2,551   & 4,913   & 7,464 \\
\hline\hline
\end{tabular}
\end{table}

@@

\begin{table}ー
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p_bar}. Correctable images had a single-valued relationship between their measured \pbar{} values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p_bar}). Galaxies with a lower-limit on \pbar{} had a non single-valued relationship (blue regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding $z$-$\mu$ bins (gray regions). Only 17\% (maximum) of FERENGI galaxies in the sample were considered ``correctable'', which is not sufficient to compute a $\zeta$ function applicable to the Hubble data.   \label{tbl:ferengi_bar_corrections}}
\begin{tabular}{lrr}
\hline \hline
				                   & N       & \% \\
\hline 
Correctable                        & 664   & 17\% \\
Lower-limi                         & 483   & 12\% \\
NEI                                & 2,803     & 71\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}
